MA_Results

### 2022-05-26 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
started epitomised

## Standards
We have identified 18 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to fix errors, incorporate new data and improve performance;
 - **Modular**: multiple models and their components can be readily combined to explore topics of more extensive scope;
 - **Epitomized**: model code is sufficiently generalised to be applied or adapted to other contexts and decision problems;
 - **Licensed**: a model's constituent parts and derivative works are persistently re-usable by other modellers; and
 - **Yielding**: a model can be deployed as a flexible and easy to use decision aid.

@@

Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both the dataset as a whole and individual files contained by that dataset. In R, code libraries can be documented with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022] and roxygen2 [@roxygen2021] that create manuals that conform to a standardised template, and pkgdown [@pkgdown2022] for creating package websites.

Guidance about how to consistently use of meaningful naming conventions when authoring code is available [@Wilson_2017; @Alarid2019]. The main logic of a program can also be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same broad type. Literate programming, where tools like RMarkdown [@xie2018r] are used to render documents that integrate computer code with plain English descriptions of each step in an analysis workflow, can make code easier to follow by both technical and non-technical users.

Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020]. The risk of these errors might be lower if there was full transparency across all steps in a study workflow. Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@@Wilson_2017].

@@

- **T1: Permanent, uniquely identified archived copies of model code and data are publicly available in open access online repositories**

@@

- **T2: Models code and data are consistently documented **<!-- Was T3 -->

- **T3: Model code is easy to follow through use of a simple and consistent syntax**<!-- Was T4 -->

- **T4: Model analyses and reporting are implemented using a literate programming approach** <!-- Was T5 -->

<!-- T6 MISSING - Deleted -->

- **T5: All parts of a study analysis and reporting workflow can be reproduced and/or replicated by third parties using publicly available materials** <!-- Was T7 -->

@@

GitHub also provides continuous integration [@CI2017] tools that can help make code updates more reliable. OSHEM developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run GitHub continuous integration checks to verify that each new version of a code library passes multiple quality tests. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

@@

Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data can reduce the risk that model revisions have unintended consequences on third party users. The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.

@@

- **I2: Model code is version controlled** <!-- Was I2 -->

- **I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured**<!-- Was I3 -->

- **I1: Model code and data use semantic versioning** <!-- Was I1 -->

- **I4: Deprecation conventions are used to retire old code / data in order to minimise the risk of unintended impacts on downstream dependencies**

### Modular Models

- **M1: Model code and data are decoupled – each is stored, managed and disseminated independently** <!-- Modified (lost ref to licensed and cited) -->

- **M2: Model code and data are distributed with explicit citation guidance**<!--Replacement - Old version now merged with E1 -->

- **M3: Model code defines encapsulating data structures**

### Epitomised Models

- **E1: Model code is distributed as libraries of functions** [compare to analysis and reporting] <!-- Modified (lost ref to OOP and merged with M2) -->

@@

- **E3: Demonstration data is available to demonstrate generalised applications of model code**

@@

- **L1: Model code is made available for re-use under either copyleft or more permissive licensing arrangements**

- **L2: Terms of use permit liberal re-use of non-confidential model data, subject to adherence to clearly specified ethical standards**

@@

@@

## Application

>>>>

## Standards
We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomized**: models can be used in multiple decision contexts;
 - **Licensed**: a model and its derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be deployed as a simple, flexible and reliable decision aid.

@@

Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its constituent individual files. In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].

Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. The main logic of a program can be made comprehensible to even non-technical users though the use of the common practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphsim [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same broad type. Literate programming, where tools like RMarkdown [@xie2018r] are used to render documents that integrate computer code with plain English descriptions of each step in an analysis workflow, can make code easier to follow by both technical and non-technical users.

An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019]. One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics.

Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020]. The risk of these errors might be lower if there was full transparency across all steps in a study workflow. Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].

@@

- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**

@@

- **T2: Model code and data are documented **<!-- Was T3 -->

- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->

- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->

- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->

- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->

@@

@@

Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users. The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.

@@

- **I1: Model code is version controlled** <!-- Was I2 -->

- **I2: Model code and data use semantic versioning** <!-- Was I1 -->

- **I3: Continuous integration is used to verify model code updates**

- **I4: Deprecation conventions are used to retire model code and data**

### Modular Models
Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013].

Many types of mental health data are highly sensitive with strict confidentiality requirements. For this reason, not all data included in some mental health models can be made widely available for others to re-use. A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.

An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [ready4oop2022].

- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->

- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->

### Epitomised Models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, 
Modular code is also recommended as good practice for scientific computing more generally [@Wilson_2017].

[model functions - compare to analysis and reporting]

- **E1: Model code is distributed as libraries of functions**  <!-- Modified (lost ref to OOP and merged with M2) -->

@@

- **E3: Test data is available to demonstrate generalised model applications**

@@

- **L1: Model code is made available for re-use under copyleft licenses**

- **L2: Non-confidential model data is available for liberal re-use, subject to adherence clearly specified ethical standards**

- **L3: Model code and data are distributed with citation tools** <!-- New -->

@@

- **Y2: Statistical models can be safely, consistently and flexibly deployed using standardised tools**

@@

# Application
